---
title: "Arron Lacey"
author: Arron Lacey
date: "`r Sys.Date()`"
bibliography: myrefs.bib
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "asis", 
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(tidyverse)
library(readxl)
library(magick)
library(glue)
library(janitor)
library(bib2df)

source("parse-citations.R")
```

```{css, echo=FALSE}
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

# Aside

```{r logo, warning = FALSE, message = FALSE, error = FALSE, fig.align = "center", out.width="50%"}
logo <- image_read("https://www.turing.ac.uk/sites/default/files/styles/people/public/2022-04/profile_photo.jpg?itok=BzOTBaea")
logo
```

## Contact {#contact}

-   <i class="fa fa-envelope"></i> [arronslacey\@gmail.com](mailto:arronslacey@gmail.com){.email}
-   <i class="fa fa-github"></i> [\@arronlacey](https://github.com/arronlacey)
-   <i class="fa fa-twitter"></i> [\@arronlacey](https://twitter.com/arronlacey)

## Skills {#skills}

**Programming:**

-   R
-   SQL
-   Python

**Research Infrastructure**

- Docker
- GitHub/GitLab
- CI/CD

**R packages**

- wandbR Weights and Biases R API - https://github.com/arronlacey/wandbR

**Selected Presentations**

- [Creating an effective learning experience (Quarto)](https://arronlacey.github.io/effective-learning-experience-talk/#/title-slide)
- [Model Tracking and Deployment (Quarto)](https://edon-initiative.gitlab.io/mlops-presentation/#/title-slide)
- [Lecture notebooks and videos](Kaggle Machine Learning MSc module code: https://www.kaggle.com/arronlacey/pm402-kaggle-resource)

**Public profiles and Websites**

  -   Turing Profile https://www.turing.ac.uk/people/arron-lacey
  -   The Turing Way: https://the-turing-way.netlify.app/welcome
  -   Carpentries AI Educators Course https://carpentries-incubator.github.io/data-science-ai-senior-researchers/
  -   Markup NLP Annotation website: https://www.getmarkup.com
  -   ResearchGate: https://www.researchgate.net/profile/Arron-Lacey

## Disclaimer {#disclaimer}

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`

# Main

## Arron Lacey, PhD {#title}

### Senior Community Manager, The Alan Turing Insitute

## Employment {data-icon="suitcase"}

```{r print-emp}
emp_data <- read_xlsx("cv-data.xlsx", sheet = "employment")

emp_data %>%
  replace_na(list(end = "present")) %>%
  # mutate_at(vars(start, end), str_replace_all, pattern = "-[0-9]*$", "") %>%
  nest(data = -c(org, institution, loc)) %>%
  mutate(print_data = map(data, function(x) {
    current <- filter(x, end == "present")
    previous <- filter(x, end != "present")
    
    prev_positions <- x %>%
      select(title:end) %>%
      separate(start, c("start_year", "start_month"), "-", convert = TRUE) %>%
      separate(end, c("end_year", "end_month"), "-", convert = TRUE,
               fill = "right") %>%
      mutate(start_month = month.name[start_month],
             end_month = map_chr(end_month, function(x) {
               if (is.na(x)) return(NA_character_)
               month.name[x]
             }),
             label = glue("{title} ({start_month} {start_year}--{end_month} {end_year})")) %>%
      pull(label) %>%
      str_replace_all("NA ", "") %>%
      as.character() %>%
      list()
    
    current %>%
      pivot_longer(contains("description"), names_to = "description_num",
                   values_to = "description") %>%
      filter(!is.na(description)) %>%
      group_by(title) %>%
      mutate(descriptions = list(description)) %>%
      ungroup() %>%
      filter(description_num == "description_1") %>%
      mutate(full_start = min(x$start)) %>%
      separate(full_start, c("start_year", "start_month"), convert = TRUE) %>%
      mutate(timeline = glue("{end} - {month.name[start_month]} {start_year}"),
             timeline = as.character(timeline),
             description_bullets = map_chr(descriptions, ~paste("-", .x, collapse = "\n")),
             prev_pos = ifelse(nrow(previous) == 0, NA_character_,
                               paste("**Position History**\n\n",
                                     map_chr(prev_positions, ~paste("-", .x, collapse = "\n"))))) %>%
      select(title, timeline, description_bullets, prev_pos)
  })) %>%
  select(-data) %>%
  unnest(cols = c(print_data)) %>%
  glue_data(
    "### {org}{ifelse(is.na(institution), '', paste(',', institution))}",
    "\n\n",
    "{title}",
    "\n\n",
    "{loc}",
    "\n\n",
    "{timeline}",
    "\n\n",
    "{description_bullets}",
    "\n\n",
    "{ifelse(is.na(prev_pos), '', prev_pos)}",
    "\n\n\n"
  )
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r print-edu}
edu_data <- read_xlsx("cv-data.xlsx", sheet = "education")

edu_data %>% 
    arrange(desc(end)) %>% 
    mutate(id = 1:n()) %>% 
    pivot_longer(
      starts_with('description'),
      names_to = 'description_num',
      values_to = 'description',
      values_drop_na = TRUE
    ) %>% 
    group_by(id) %>% 
    mutate(
      descriptions = list(description)
    ) %>% 
    ungroup() %>% 
    filter(description_num == 'description_1') %>% 
    mutate(
      timeline = ifelse(
        is.na(start) | start == end,
        end,
        glue('{end} - {start}')
      ),
      description_bullets = map_chr(descriptions, ~paste('-', ., collapse = '\n')),
    ) %>% 
    mutate_all(~ifelse(is.na(.), 'N/A', .)) %>% 
    glue_data(
      "### {title}",
      "\n\n",
      "{institution}",
      "\n\n",
      "{loc}",
      "\n\n",
      "{timeline}", 
      "\n\n",
      "{description_bullets}",
      "\n\n\n",
    )
```

### Selected Publications {data-icon="award" data-concise="true"}

---
nocite: '@*'
...
